Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-03 tex/VHzQ.tex
Continued wee progress

There are 14 objects that have no NIR detections.  3 of these
(PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
been observed (by VHS) but are out of our queried time range.  6
objects have not been observed (or at least the data is not in the
WSA/VSA archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too
far north for UKIRT and cannot be observed.

@@

For the 278 VH$z$Q with coverage detections, the mean number of
exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
minimum number of exposures 17 and 12, and the maximum number or
exposures being 114 (for both bands).  For the W3/4 filters, the
corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
5.8 and 6.8 and 69 (for both bands). These values are direclty from
the {\tt w$x$cov} enteries in the 
\href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.

@@

\begin{table}
\centering
\begin{tabular}{l r  r}
\hline \hline
$z \geq$  & Age / Myr & No. of objects \\
\hline 
7.50         &    700         &   1   \\
7.00         &    767         &   4   \\
6.78         &    800         &  14   \\
6.50         &    845         &  40   \\
6.19         &   900          &  86   \\
6.00         &   937          &  170   \\
5.70         & 1000          &  267   \\
5.00         & 1180          &  463   \\
\hline \hline
\end{tabular}
\caption{The number of objects at or above a given redshift. 
The age of the Universe in megayears is also given. }
      \label{tab:ages}
\end{table}

@@

    %\subsubsection{
    Very High-$z$ Quasars Detected in WISE W3 and W4.

@@

\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m_{\rm accr}}$. A consequence of this would be that these quasar exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra. We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
    Y and H are almost uniform, but the coverage is much less.}
  \label{fig:1}
\end{figure}

>>>>

There are 14 objects that have no NIR detections.  3 of these
(PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
been observed (by VHS) but are out of our queried time range.  6
objects have not been observed (or at least the data is not in the
WSA/VSA archives yet) and 5 objects at declination $\delta \geq +60$
deg are too far north for UKIRT and cannot be observed.

@@

For the 278 VH$z$Q with coverage detections, the mean number of
exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
minimum number of exposures 17 and 12, and the maximum number or
exposures being 114 (for both bands).  For the W3/4 filters, the
corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
5.8 and 6.8 and 69 (for both bands). These values are direclty from
the {\tt w$x$cov} enteries in the WISE
\href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.

@@

@@

Very High-$z$ Quasars Detected in WISE W3 and W4.

@@

\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well
have have large values of changing mass accretion rate, $\ddot{m}_{\rm
accr}$. A consequence of this would be that these quasar exhibit signs
of variability, most likely showing up in their UV/optical rest-frame
spectra. We look for evidence of this variability signature in the NIR
and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_J_abMagLim.png}
  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
    Y and H are almost uniform, but the coverage is much less.}
  \label{fig:1}
\end{figure}
